사람과 기계의 일자리 경쟁 요인과 협업 방안

### 2020-04-14 tutorial/paper/paper.Rmd

```{r tax-exam, eval=FALSE}
library(tidyverse)
library(rvest)

tax_url <- "http://www.wcpa.co.kr/cta/info_ystats.php"

# Sys.setlocale("LC_ALL", "C")

exam_df <- tax_url %>% 
  read_html() %>% 
  html_node(xpath = '/html/body/div[1]/div[2]/div/div[2]/div[2]/div/ul[2]/li/div/table') %>% 
  html_table(fill = TRUE)

# Sys.setlocale("LC_ALL", "Korean")

exam_df %>% 
  gather(year, value, -`구분`) %>% 
  filter(구분 == "합격자") %>% 
  select(연도=year, 합격자=value) %>% 
  knitr::kable(format = "latex", booktabs = TRUE)

@@

```{r fred-data-labor-participation, dev="cairo_pdf", out.width="100%",  eval=FALSE}
library(fredr)
library(xts)
fredr_set_key(FRED_KEY)

@@

```{r labor-share-test, dev="cairo_pdf", out.width="100%", fig.cap="TESTING"}
labor_share <- tribble(~"date",	~"share",
"1948-01-01",	"49.3",
"1949-01-01",	"49.7",
"1950-01-01",	"49.3",
"1951-01-01",	"49.9",
"1952-01-01",	"50.9",
"1953-01-01",	"51.6",
"1954-01-01",	"50.9",
"1955-01-01",	"50.1",
"1956-01-01",	"50.7",
"1957-01-01",	"50.6",
"1958-01-01",	"50.2",
"1959-01-01",	"49.8",
"1960-01-01",	"50.2",
"1961-01-01",	"49.8",
"1962-01-01",	"49.5",
"1963-01-01",	"49.3",
"1964-01-01",	"49.3",
"1965-01-01",	"49.0",
"1966-01-01",	"49.5",
"1967-01-01",	"50.1",
"1968-01-01",	"50.3",
"1969-01-01",	"51.0",
"1970-01-01",	"51.6",
"1971-01-01",	"50.6",
"1972-01-01",	"50.2",
"1973-01-01",	"49.9",
"1974-01-01",	"50.2",
"1975-01-01",	"48.7",
"1976-01-01",	"48.5",
"1977-01-01",	"48.2",
"1978-01-01",	"48.1",
"1979-01-01",	"48.5",
"1980-01-01",	"48.8",
"1981-01-01",	"47.7",
"1982-01-01",	"47.6",
"1983-01-01",	"46.9",
"1984-01-01",	"46.2",
"1985-01-01",	"46.3",
"1986-01-01",	"46.7",
"1987-01-01",	"46.9",
"1988-01-01",	"46.6",
"1989-01-01",	"46.3",
"1990-01-01",	"46.7",
"1991-01-01",	"46.4",
"1992-01-01",	"46.3",
"1993-01-01",	"45.9",
"1994-01-01",	"45.3",
"1995-01-01",	"45.3",
"1996-01-01",	"45.1",
"1997-01-01",	"45.2",
"1998-01-01",	"45.8",
"1999-01-01",	"46.1",
"2000-01-01",	"46.6",
"2001-01-01",	"46.3",
"2002-01-01",	"45.3",
"2003-01-01",	"44.8",
"2004-01-01",	"44.3",
"2005-01-01",	"43.4",
"2006-01-01",	"43.2",
"2007-01-01",	"44.3",
"2008-01-01",	"44.9",
"2009-01-01",	"43.8",
"2010-01-01",	"42.6",
"2011-01-01",	"42.4",
"2012-01-01",	"42.1",
"2013-01-01",	"41.9",
"2014-01-01",	"41.9",
"2015-01-01",	"42.5",
"2016-01-01",	"42.9",
"2017-01-01",	"43.2",
"2018-01-01",	"43.2")

>>>>

@@

```{r fred-data-labor-participation, dev="cairo_pdf", out.width="100%"}
library(fredr)
library(xts)
fredr_set_key(FRED_KEY)

@@
